Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2013-11-16 paper.tex
added minor

More ambitiously, our techniques might allow analysis of non-data aided channel estimators for modern communications systems such as mulitple anntannae systems~\cite{4138046}, and systems employing orthogonal frequency division multiplexing.  We see the results presented here as a starting point for an potentially potent approach to the analysis of channel estimators that is complementary to the commonplace method of comparing results of Monte-Carlo simulations with Cramer-Rao lower bounds.

>>>>

More ambitiously, our techniques might allow analysis of non-data aided channel estimators for modern communications systems such as mulitple anntannae systems, and systems employing orthogonal frequency division multiplexing~\cite{4138046,Heath99exploitinginput}.  We see the results presented here as a starting point for a potentially potent approach to the analysis of channel estimators that is complementary to the commonplace method of comparing results of Monte-Carlo simulations with Cramer-Rao lower bounds.
